THESIS PROJECT PROPOSAL

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino, second generation consist of charm quark, strange quark, muon and muon neutrino and the third generation of matter particles has top quark, bottom quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be produced at the particle colliders like the Large Hadron Collider in Geneva. There are various production modes of Higgs boson like the gluon gluon fusion(ggF), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.

>>>>

The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino,
second generation consist of charmquark, strange quark, muon and muon neutrino and the third generation of matter particles has
top quark,bottom quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which 
mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the standard model called
the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be produced at the particle
colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs boson like the gluon gluon 
fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top
quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). Each production channel has its
own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons. The Higgs boson can also
decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of W
bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a photon. It is also interesting
to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering 
cross section like in the Higgs-portal dark matter models.

The main production mode of higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons can only proceed via loop diagrams which involve vector bosons or heavy quarks in the loop.
